How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-15 tse-paper/content.tex
improve study results

\subsubsection{Retrieved Information}
The information that was targeted is presented in
\Cref{fig:litsur:info_target} varied from article to article.
Most prominent was the search for errors (39\%) that occured within
the build process, followed by extracting the executed or the failing
tests (both 11\%).
There were also numerous cases which targeted more specialized
information, such as the environments used during the
build~\cite{zolfagharinia2017not}, packages
installed~\cite{selberg2012use} or hints to source files which are
related to build failures~\cite{ren2018automated}.

In most cases (51\%), a chunk was retrieved from the log.
Cemencic and Couturier~\cite{clemencic2014new}, for example,
scan build logs for compilation errors, while Zhang et
al.~\cite{zhang2016android} retrieve the duration of
tasks within the build.

The articles classified the build logs into categories in 36\% of
the cases.
Didrik Lindqvist~\cite{lindqvist2019detection} used build logs to
distuinguish failures caused by
developers from those caused by infrastructure, while
Kavaler et al.~\cite{kavaler2019tool} idenfity projects that use
automated static analysis tools.
Other types of information (e.g.\ counting
lines, summarization) were only retrieved
in one case each.

@@

\subsubsection{Retrieval Technique}
\Cref{tab:litsur:techniques} presents the techniques which the articles
described for processing build logs.
43 of the 61 articles we inspected touched on how they are analyzing build
logs.
However, only 16 of these described their method in detail.

The most mentioned method (34\%) was using a parser, where we also
included
rather unprecise statements like ``we parse the build logs''.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning techniques such as natural language
processing or information retrieval techniques.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They start with manual categorization of the build logs and select
search strings that identify their targeted categories.
Based on the search strings they create a script which automatically
classifies the remaining logs.
%TODO: they are not actually in our survey, the talk about 'test logs'
Amar et al.~\cite{amar2019mining} compare different approaches to
reduce the number of lines to be inspected by the developer.
Their best performing technique creates a diff between the logs from a
successful and a failed build and ranks the remaining lines using
Information Retrieval (IR) techniques.

25\% of the articles claimed their implementation is available, however we
saw very low reuse of build log analysis tools within our survey.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent}, two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.

@@

\subsubsection{Build Logs}
The distribution of supported build tools is shown in
\Cref{fig:litsur:log_producer}.
Of the articles we surveyed, 30\% analyzed build logs produced by
Maven~\cite{maven2019website}, 16\% ones produced by
Gradle~\cite{gradle2020website}
and 10\% logs produced by Ant~\cite{ant2020website}.

>>>>

\subsubsection{Retrieved Information}
The information that was targeted varied from article to article.
Most prominent was the search for errors (39\%) which occured within
the build process, as presented in \Cref{fig:litsur:info_target}.
This is followed by extracting the executed or the failing
tests (both 11\%).
There were also numerous cases which targeted more specialized
information, such as the environments used during the
build~\cite{zolfagharinia2017not}, packages
installed~\cite{selberg2012use} or hints to source files which are
related to build failures~\cite{ren2018automated}.

In most cases (51\%), a chunk was retrieved from the log.
Build logs were scanned for compilation
errors~\cite{clemencic2014new} or
the duration of tasks within the build~\cite{zhang2016android}.
36\% of the articles classified the build logs into categories.
For instance distinguishing failures caused by developers from
failures casued
by infrastructure errors~\cite{lindqvist2019detection} or
whether projects use automated statc analysis
tools~\cite{kavaler2019tool}.
Other types of information (e.g.\ counting
lines, summarization) were only retrieved
in one case each.

@@

\subsubsection{Retrieval Technique}
\Cref{tab:litsur:techniques} presents the techniques that the articles
described for processing build logs.
43 of the 61 articles we inspected mentioned how they are analyzing build
logs.
However, only 16 of these described their method in detail.

The most mentioned method (34\%) was using a parser, where we also
included
rather unprecise statements like ``we parse the build logs''.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning techniques such as natural language
processing or information retrieval techniques.
To give examples,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They start with manual categorization of the build logs and select
search strings that identify their targeted categories.
Based on the search strings they create a script which automatically
classifies the remaining logs.

25\% of the articles claimed their implementation is available,
however we
saw very low reuse of build log analysis tools within our survey.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an extended version of them~\cite{rott2019empirische,
shi2018evaluating},
two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.

@@

\subsubsection{Build Logs}
The distribution of supported build tools is shown in
\Cref{fig:litsur:log_producer}.
Of the articles we surveyed, 30\% analyzed build logs produced by
Maven~\cite{maven2019website}, 16\% analyzed logs produced by
Gradle~\cite{gradle2020website}
and 10\% analyzed logs produced by Ant~\cite{ant2020website}.
